# Grant's Tomb (Journal Entry)

```{r}
grants_old <- "https://s3.trueloveserver.com/arthum/GrantsTomb.jpg"
```
![Old depiction of the tomb](`r grants_old`)


My first thought when viewing Grant’s memorial is a sense of power and strength. In a sense, it almost feels like a fortress that the general is defending

## The Columns
To begin, there are noticeable columns through the building. There are two
layers of columns and an additional set of statues above both which look
like columns from afar, although they are more decorative (they are eagles
but actually look like axes from a medium distance). The bottom columns
remind me of the Egyptian architecture that the Parthenon strayed away
from in surrounding the building. They are at the front, and closely resemble
many of the features that we talked about in the Parthenon. They taper on
the way up, and have a connecting piece (the capital) somewhat similar to
the Parthenon, although more box like.


However, many of the features that we discussed about the columns and
their effects are absent from the Sculpture. Noticeably, the columns do not
give a sense of porosity and openness. They do feel weight bearing but
not nearly as welcoming as someone had mentioned in class. The structure
doesn’t have the same post and lentil feel. It feels like a solid four-walled
fortress with columns in the front and around the top dome for decoration.
Maybe to support the sort-of balcony if anything.

## The pediment resembling statues

Of quick mention is the somewhat of a pediment that feels very triangular
like that of the Parthenon. Although it is much further simplified (as does
the rest of the sculpting feel on this tomb). Also noticable is the use of words
rather than just sculptures. ”LET US HAVE PEACE” is at the center, and
seems to draw the eye as the center of the sculpture. Unlike the Parthenon,
the pediment doesn’t seem to add to the grandness of the statue. It seems
to make a simple statement about the wishes of those that lay within.



```{r}
grants_modern <- "https://s3.trueloveserver.com/arthum/grants_tomb_modern.JPG"
```
![Modern Day picture of the tomb](`r grants_modern`)

## The Eagles?
The almost dragon-like eagles quickly drew my attention. Of the animals
present on the Parthenon, I do not recall any bird. After quick research, it
turns out the eagles are a relatively new decoration, (donated by the New
York City Post Office in the 30’s); this explains why they are not seen in the
post card image above but are shown below in a modern photo.



The eagles however don’t feel like a sign of democracy or a welcoming
entrance to a war hero of the country. They feel imposing, almost like they stand guard to the entrance of the fallen general and his wife.

## The Dome
In some sense, the tomb feels like it has a Parthenon/Egyptian
inspiration on bottom with the capital dome put on top. The capital dome
having been completed just 31 years prior, I don’t think it is a stretch to
believe it was the inspiration for the classical column surrounded dome on
top. Noteably, it provides some of the openness that the Parthenon provided
through its use of encompassing columns.


Two pieces naturally belong together. The bottom fortress and top resemblance of democracy I think must be purposeful. It shows a joining of
politics and war, a uniting of the country through a man who served both
as a leading general and as president of it. It shows both sides of the fallen
president and is all set in marble, a material of permanence as we discussed
in class.